True lies

### 2018-11-03 GSV-comment-brief.Rmd
Use posterior highest density region; split out GSV methods into separate file; remove different estimation targets; rewrite...

---
title: "Lies and the lying liars who tell them"
subtitle: "Comment on Garbarino, Slonim and Villeval (2018)"
author: "David Hugh-Jones"
date: "`r Sys.Date()`"
header-includes:
  - \usepackage{setspace}
  - \usepackage{placeins}
  - \onehalfspacing
  - \usepackage{fontspec}
output:
  pdf_document:
    md_extensions: +raw_attribute
    latex_engine: xelatex
  tufte::tufte_handout:
    latex_engine: xelatex
    md_extensions: +raw_attribute
  bookdown::tufte_handout2:
    latex_engine: xelatex
    md_extensions: +raw_attribute
  bookdown::tufte_html2: 
    pandoc_args: ['--self-contained']
    keep_intermediates: true
bibliography: bibliography.bib
link-citations: yes
fontsize: 12pt
mainfont: Times New Roman
mathfont: Times New Roman
---

>  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution 
>  of the number of liars in "coin flip" style experiments. However, their method  
>  gives misleading confidence intervals. I explain why, and describe two better
>  ways to calculate probability distributions.

@@

library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(echo = FALSE)
options(huxtable.knitr_output_format = "latex")
source("bayesian-heads-cts.R")
suppressPackageStartupMessages({
  library(Hmisc)
  library(magrittr)
  library(dplyr)
  library(purrr)
  library(tidyr)
  library(readr)
  library(ggplot2)
  library(broom)
  library(huxtable)
  loadNamespace("MASS")
})

huxtable::set_default_properties(position = "left", top_padding = 12, bottom_padding = 6)
set.seed(19751027)

@@

# if TRUE, the number of liars in each simulation is randomly drawn
# from a population with `Liars` liars.
# If FALSE, the number of liars is fixed at `Liars * N`.
# If you change this, you may need to recreate the simulations CSV file
sample_from_pop <- TRUE

# if FALSE, use L/N as ground truth;
# if TRUE, use (R-heads)/(N-heads):
estimate_lies_not_liars <- FALSE

if (sample_from_pop && estimate_lies_not_liars) {
  stop("Can't estimate proportion of actual lies in population!")
}

params <-   list(
  N     = c(10, 50, 100, 500),
  Liars = seq(0, 1, 0.1),
  P     = c(.2, .5, .8)
)

@@

method_used_statement <- paste0("This paper can be recreated from the .Rmd file using different ",
      "methods to calculate confidence interval coverage and squared errors. 'Ground ",
      "truth' can be the population proportion of liars, the sample proportion of liars or ",
      "the sample proportion of actual lies. Ground truth for the document you are reading was: ",
        if (sample_from_pop) "the population proportion of liars." else 
        if (estimate_lies_not_liars) "the sample proportion of actual lies." else 
        "the sample proportion of liars."
      )

if (! sample_from_pop && ! estimate_lies_not_liars) method_used_statement <- ""

@@

TODO XXX: point out the claims they make. Add your sims of when the posterior is wrong
and intervals fail even for (R-T)/(N-T). Convert to sampling from a cts distrib.

**`r method_used_statement`**

@@

A naïve estimate would be that if e.g. 80 people of 100 report heads, then on average 50 really saw
heads and 60% (30/50) of the remainder are lying. More generally, from *R* reports of a good outcome
in a sample of size *N*, where the _bad_ outcome happens with probability *P*, we can estimate that
a proportion $\frac{R/N - (1-P)}{P}$ are lying [@abeler2016preferences]. The problem with this approach is that the number of heads is not
fixed. If we see 1 out of 3 people reporting heads, this method estimates there are less than zero
liars. But it is still possible that everyone saw heads and 1 person lied.

@@

sim_data <- tidyr::crossing(
  N     = params$N,
  Liars = params$Liars,
  P     = params$P
)
sim_data$Liars_pop_pct <- sim_data$Liars

@@

if (sample_from_pop) {
  sim_data %<>% 
        group_by(N, Liars, P) %>% 
        mutate(
          Liars_sample = rbinom(n(), N, Liars)
        ) %>% 
        ungroup() %>% 
        mutate(
          Liars = Liars_sample,
          Liars_sample = NULL
        )
} else { 
  sim_data$Liars <- round(sim_data$Liars * sim_data$N, 0)
}

simulate_cointoss <- function (row) {
  h_liars <- rbinom(1, row["Liars"], 1 - row["P"])
  h_honest <- rbinom(1, row["N"] - row["Liars"], 1 - row["P"])
  R <- row["Liars"] + h_honest
  names(R) <- NULL
  heads <- h_honest + h_liars
  c(R = R, heads = heads)
}

results <- apply(sim_data, 1, simulate_cointoss)

sim_data$R <- results["R", ]
sim_data$heads <- results["heads",]

sim_data <- sim_data %>% arrange(N, Liars, P)

nci_levels <- length(ci_levels)
sim_data <- sim_data[rep(seq_len(nrow(sim_data)), each = nci_levels), ]
sim_data$CI <- rep(ci_levels, nrow(sim_data)/nci_levels)

sim_data$P <- sim_data$P * 100 # input has to be in %

# algorithm is deterministic so we save time by 
# only printing out distinct lines
sim_output <- sim_data %>% 
      select(N, R, P, CI) %>% 
      distinct()

file_root <- paste0("GSV-sims", if (sample_from_pop) "-pop-sample")
sim_output_file <- paste0(file_root, "Output.csv")
if (rerun_java) {
  sim_input_file <- paste0(file_root, ".csv")
  readr::write_csv(sim_output, path = sim_input_file)

@@

```{r sanity-checks, include = FALSE, cache = cache_results}
sim_data %<>% mutate(
  expected_R = Liars + (1 - P/100) * (N - Liars)
)
summary(lm(R ~ expected_R, sim_data))
sim_data %>% 
      group_by(P, N) %>% 
      do(
        broom::tidy(lm(R ~ expected_R, .))
      ) %>% 
      filter(term == "expected_R")

@@

sim_est <- left_join(sim_est, gsv_estimates, by = c("N", "R", "P", "CI"))

@@

bayes_est <- sim_output %>% 
      rowwise() %>% 
      do({
        pstr <- update_prior(
                heads = .$R, 
                N = .$N, 
                P = .$P/100, 
                prior = my_prior
              )
        ci <- .$CI / 100
        ci_qs <- c(1/2 - ci/2, 1/2 + ci/2)
        cis <- dist_quantile(pstr, ci_qs)
        # calculate quantities as prop dishonest
        tibble(
          EV.ubayes = dist_mean(pstr),
          LB.ubayes = cis[1], 
          UB.ubayes = cis[2]
        )
      })
bayes_est <- cbind(sim_output, bayes_est)
sim_est <- left_join(sim_est, bayes_est, by = c("N", "P", "R", "CI"))

@@

simple_est <- sim_output %>%
      mutate(
        EV.simple = heads_to_liars(R/N, P/100)
      )

heads_confints <- apply(sim_output, 1, function (row) {
  ci <- binom.test(row["R"], row["N"], conf.level = row["CI"]/100)$conf.int
  res <- heads_to_liars(ci, row["P"]/100)
  names(res) <- c("LB.simple", "UB.simple")
  res
})

@@

```{r recalculate-gsv-functions}

dist_L_gsv <- function(heads, N, P) {
  # L liars means that T = heads - L
  # T is distributed binomially conditional on being no more than `heads`
  L = 0:heads
  result <- rep(NA_real_, length(L))
  result <- dbinom(heads - L, N, 1 - P) / sum(dbinom(L, N, 1 - P))

  result
}

prop_liars <- function(L, heads, N) {
  stopifnot(all(L <= heads), heads >= 0, heads <= N)
  # for any number of liars L, reported heads, and N:
  # true heads T = heads - L
  # number observing low outcome = N - T
  # proportion lying is L/(N-T)
  T <- heads - L
  prop_lied <- L/(N - T)
  prop_lied[N == T] <- 1 # if everyone saw true heads, then   
                         # we can't estimate how many might have
                         # GSV code solves this by assuming 1

  prop_lied
}

prop_liars_ci_gsv <- function (ci, heads, N, P) {
  stopifnot(0 <= ci, ci <= 1, heads <= N, 0 <= heads, 0 <= P, P <= 1)

  dist_L <- dist_L_gsv(heads, N, P)
  stopifnot(length(dist_L) == heads + 1)

  pl <- prop_liars(0:heads, heads, N)
  stopifnot(length(pl) == heads + 1)

  pl <- pl[dist_L > 0] # get rid of 0-probability events
  dist_L <- dist_L[dist_L > 0]
  dist_L <- dist_L[order(pl)]
  pl <- sort(pl)

  cdf <- cumsum(dist_L)

  # we know pl is always positive, so represent that:
  cdf <- c(0, cdf)
  pl  <- c(0, pl)

  tail <- (1 - ci)/2
  # lower bound: no more than tail% of probability has less than this
  lb_idx <- max(which(cdf <= tail)) # must exist since cdf starts at 0.
  lb <- pl[lb_idx]

  # upper bound: no more than 1-tail% of probability has more
  ub_idx <- min(which(cdf >= 1 - tail))
  ub <- pl[ub_idx]

  return(c(lb, ub))
}

prop_liars_ev_gsv <- function(heads, N, P) {
  dist_L <- dist_L_gsv(heads, N, P)
  prop_lied <- prop_liars(0:heads, heads, N)
  sum(dist_L * prop_lied)
}
```

```{r check-gsv-posterior, eval = FALSE}

# if we assume that liars are not uniformly distributed, the posterior of number of heads
# is not like the prior
N <- 10
CI <- 0.9
tmp <- replicate(10000, {
  # L <- sample(1:N, 1) # for this, always accurate?
  L <- rbinom(1, N, 0.1) # not many liars
  HL <- rbinom(1, L, 0.5)
  HNL <- rbinom(1, N-L, 0.5)
  R <- L + HNL
  H <- HL + HNL
  c(L, R, H, N, CI, prop_liars_ci_gsv(CI, R, N, 0.5))
})

tmp <- as.data.frame(t(tmp))
names(tmp) <- c('L', 'R', 'H', 'N', 'CI', 'cilo', 'cihi')
tmp$lies_told <- with(tmp, (R-H)/(N-H))
tmp$lies_in_ci <- tmp$cilo <= tmp$lies_told & tmp$lies_told <= tmp$cihi

# the prior:
ggplot(tmp, aes(H)) + geom_bar(aes(y = calc(prop))) + 
  geom_line(data = tmp[tmp$R > quantile(tmp$R, 0.8), ], aes(H, calc(prop)))
# the posterior is not the prior:
hist(tmp$H, col = "grey", breaks = 0:N, freq = FALSE, ylim = c(0, 1))
hist(tmp$H[tmp$R==10], breaks = 0:N, add= T, freq = FALSE, col = rgb(1,0,0,.5))

# the posterior:
lines(density(with(tmp, H[R > quantile(R, 0.9)])))

# how accurate are we for different numbers of R.
# NB you can also judge accuracy by different numbers of H, but I'm not sure that's fair as H is
# an unknown parameter - maybe it is like saying "confidence interval coverage is way off when
# the errors are big!"

GSV_coverage <- tmp %>% group_by(R) %>% 
  summarize(n_sims = n(), coverage = mean(lies_in_ci))

tmp %<>% left_join(GSV_coverage, by = "R")

scale_fac <- max(tmp$n_sims)
ggplot(GSV_coverage, aes(R)) + 
    geom_hline(yintercept = CI, linetype = 2) +
    geom_line(aes(y = coverage), colour = "red") +
    geom_line(aes(y = n_sims/scale_fac), colour = "grey") +
    scale_y_continuous(sec.axis = sec_axis(~.*scale_fac, name = "N sims"))

plot(GSV_coverage$R, GSV_coverage$coverage, type = "l")
# number of cases:
points(GSV_coverage$R, GSV_coverage$n_sims/max(GSV_coverage$n_sims), type = "h", col = "grey")

table(low_coverage = tmp$coverage < 0.8, tmp$R > 60) %>% prop.table(2)
```

@@

sim_tmp <- sim_output[, c("R", "N", "P", "CI")]
recalc <- apply(sim_tmp, 1, function (x) {
  x <- c(
    prop_liars_ev_gsv(x["R"], x["N"], x["P"]/100),
    prop_liars_ci_gsv(x["CI"]/100, x["R"], x["N"], x["P"]/100)
  )
  names(x) <- paste0(c("EV", "LB", "UB"), ".recalc")
  x
}) 
sim_tmp <- cbind(sim_tmp, t(recalc))
sim_est <- left_join(sim_est, sim_tmp, by = c("N", "P", "R", "CI"))

@@

# alternative "ground truths":
if (estimate_lies_not_liars) {
  sim_est %<>% mutate(
          true_prop = (R - heads)/(N - heads)
        )
} else if (sample_from_pop) {
  sim_est %<>% mutate(
          true_prop = Liars_pop_pct
        )
} else {
  sim_est %<>% mutate(
          true_prop = Liars/N
        )
}

sim_est %<>% mutate(
        within_ci = true_prop >= LB & true_prop <= UB,
        error     = EV - true_prop,
        error_sq  = error^2
      )

@@

I ran simulations to check the overall performance of the GSV confidence intervals. Simulations
parameters are shown in Table \ref{tab:params-table}. For each parameter combination, I ran 1000
simulations. "Liars" always reported heads. Non-liars reported tails with probability *P* and
heads otherwise. For each simulation and confidence interval, I computed whether the confidence interval 
contained the true value of *L/N*. Table \ref{tab:coverage-overall} shows the results.

@@

huxtable(
        Parameter = c(
          "Sample size (N)", 
          "Proportion of liars (L/N)", 
          "Probability of bad random outcome (P)"
        ),
        Values    = c(
          paste(params$N, collapse = ", "),
          paste(params$Liars, collapse = ", "),
          paste(params$P, collapse = ", ")
        ),
        add_colnames = TRUE
      ) %>% 
      set_caption("Parameter values") %>% 
      set_label("tab:params-table") %>% 
      theme_plain()
```

@@

ht_just_gsv <- ht_overall[1:2,]
ht_just_gsv[1, 1] <- ""
theme_plain(ht_just_gsv)
```

By definition, 95% of 95% confidence intervals ought to contain the true value, on average. This
is called "achieving nominal coverage". GSV
intervals are far from this. The confidence intervals are too narrow. Further analysis shows that
this problem holds across all simulated probabilities of the low outcome *P*, confidence
levels, and sample sizes *N* (up to 500).^[See the appendix.]

@@

\[
Z_{T,R,N,p} = \frac{
  \textrm{binom}(T,N,p)
}{
  \sum^R_{k=0}\textrm{binom}(k,N,p)
}
\]

This is the binomial distribution, truncated at *R*, because by assumption, nobody "lies downward"
and reports tails when they really saw heads.

Next, from *T* the number of liars is calculated as *R-T*; and the proportion of liars is calculated
as *(R-T)/(N-T)*, because *N-T* people saw the low outcome and had the chance to lie. Combining this
with the truncated binomial gives a cumulative distribution function of the proportion of liars.
This can then be used to estimate means and confidence intervals.

Putting these together, for *R = N = 10*, the estimated distribution of liars is calculated as follows:

* With probability $\frac{1}{1024}$, there were really *T = 10* heads. Nobody lied in the sample.^[But  the proportion of people who lied *out of those who saw tails* is undefined, because noone saw tails. The 
GSV software seems to resolve this by fixing the proportion of lies to 100%.]

@@

First, if 10 out of 10 heads are reported, you should learn two things. On the one hand, there
are probably many liars in your sample. On the other hand, probably a lot of coins really landed heads.
The probability distribution above does not take account of this. In particular, for *R = N*, 
the equation above reduces to the binomial distribution. This is not correct.

Second, more importantly, the GSV approach estimates the distribution of the proportion of 
*lies actually told*, among the subsample of people who saw tails:

\[
\textit{Lies} = \frac{R-T}{N-T} 
\]

But usually, we are not interested in the proportion of
lies actually told. We care about how many people in the sample *are liars*, who would lie if they
saw tails:

\[
\textit{Liars} = \frac{L}{N}.
\]

We care about *Liars* not *Lies*, because *Lies* is just a noisy estimate of *Liars*: it is the
number of liars who happened to see heads. It is a function of honesty and luck. We are interested
in the honesty.^[There may be times when social scientists care about how many people actually
lied, but I cannot think of many.]

Suppose *R = 10* heads out of 10 are reported, and suppose 9 heads were really observed, *T = 9*.
*Lies* is indeed 100%.  But it is 100% of 1 person
-- the only person who saw tails. That one person's behaviour is an unbiased estimate of the
proportion of liars in the sample, *Liars*. But it is a very noisy estimate.

The first problem means that when *R* is very high or low,
the percentage of confidence intervals containing *Lies*
may fall off sharply.^[Depending on the distribution of the number of liars *L*.]

The second problem means that the percentage of confidence intervals containing *Liars*
is almost always much less than the nominal coverage.

@@

as_huxtable(coverage_rn, add_colnames = TRUE) %>% 
      set_caption("GSV confidence interval coverage by low and high R/N") %>% 
      set_label("tab:coverage-rn") %>% 
      set_escape_contents(2:3, 1, FALSE) %>% 
      set_number_format(-1, -1, list(pct_format)) %>% 
      theme_plain()
```

@@

Can we do better? There are two alternative methods one might use to calculate confidence intervals.
The first is simply to calculate confidence bounds for the proportion of
heads that would be reported in the population, given the number that were reported in the sample. 
One can then back out
confidence bounds for the proportion of liars as $\frac{R/N - (1-P)}{P}$, as in
@abeler2016preferences.^[Confidence bounds lower than 0 can be set to 0.]  As GSV point out, this
assumes that the sample proportion of high outcomes was equal to its expected proportion. We'll see 
whether this matters.

@@

The second method is to use Bayes' rule. Start with a prior probability distribution over
the number of liars *L*, *Pr(L)*. The posterior probability is then:

\[
\textrm{Pr}(L | R; N,P) = \frac{
  \textrm{Pr}(R|L; N,P) \textrm{Pr}(L)
}{
  \sum_{L'=0}^N \textrm{Pr}(R|L'; N,P) \textrm{Pr}(L')
}
\]

where the probability of getting *R* reports of heads in total for given *L* is just
the probability that the *N - L* honest people saw *R - L* heads:

\[
\textrm{Pr}(R|L; N,P) = \textrm{binom}(R - L, N - L,1 - P)
\]

One can then estimate the proportion of *Liars* as *L/N*. From
this, one can derive confidence intervals and expected values in the usual way.

For the estimation here, I used a uniform prior, with *Pr(L) =* $\frac{1}{N+1}$ for *L* in  0
to *N*.

I used these estimation methods on my simulated data. Results are shown in Table
\ref{tab:coverage-allmethods}. Both frequentist and  Bayesian methods mostly achieve the nominal
confidence level, with more than 90/95/99% of intervals containing the true value of *Liars*. The
exception is the frequentist 99% confidence interval, which is too narrow.

@@

as_huxtable(coverage_N, add_colnames = TRUE) %>% 
      set_rowspan(c(2, 4, 6), "Method", 2) %>% 
      set_valign(c(2, 4, 6), "Method", "top") %>% 
      set_number_format(-1, contains("CI"), list(pct_format)) %>% 
      set_caption("Confidence interval coverage by sample size") %>% 
      set_label("tab:coverage-N") %>% 
      theme_plain() %>% 
      set_bottom_border(6, 1, 0.4)
```

@@

ggplot(nats, aes(x = factor(resnat, levels = resnat), y = mean, fill = mean)) +
      geom_col(alpha = 0.8) +
      geom_linerange(aes(ymin = ci.low,ymax = ci.high)) +
      geom_point(aes(y = prop_liars), shape = 4, size = 3) +
      xlab("Nation") + ylab("Prop. liars") +
      viridis::scale_fill_viridis(option = "E", guide = FALSE) + 
      theme_light() +
      coord_flip()

@@

Table \ref{tab:country-comparisons} shows Bayesian comparisons for selected countries. Even though
estimates have "shrunk" towards the pooled mean from the naive estimates, differences remain
significant, partly because the pooled prior has made posterior confidence intervals narrower.

>>>>

---
title: "True lies"
subtitle: "Comment on Garbarino, Slonim and Villeval (2018)"
author: "David Hugh-Jones"
date: "`r Sys.Date()`"
header-includes:
  - \usepackage{setspace}
  - \usepackage{placeins}
  - \onehalfspacing
  - \usepackage{fontspec}
output:
  pdf_document:
    md_extensions: +raw_attribute
    latex_engine: xelatex
  tufte::tufte_handout:
    latex_engine: xelatex
    md_extensions: +raw_attribute
  bookdown::tufte_handout2:
    latex_engine: xelatex
    md_extensions: +raw_attribute
  bookdown::tufte_html2: 
    pandoc_args: ['--self-contained']
    keep_intermediates: true
bibliography: bibliography.bib
link-citations: yes
fontsize: 12pt
mainfont: Times New Roman
mathfont: Times New Roman
---

>  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution 
>  of the number of lies told in "coin flip" style experiments. I show that their estimates and
>  confidence intervals are flawed. I explain why, and describe two better
>  ways to estimate the probability distribution of the proportion of liars.

@@

library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(echo = FALSE)
options(huxtable.knitr_output_format = "latex")

source("bayesian-heads-cts.R")
source("GSV-heads.R")

suppressPackageStartupMessages({
  library(Hmisc)
  library(MASS)

  library(dplyr)
  library(purrr)
  library(broom)
  library(readr)
  library(magrittr)
  library(tidyr)
  library(ggplot2)

  library(huxtable)
  library(hdrcde)
})

huxtable::set_default_properties(position = "left", top_padding = 12, bottom_padding = 6)
ggplot2::theme_set(theme_light())

set.seed(19751027)

@@

params <-   list(
  N      = c(10, 50, 100, 500),
  lambda = seq(0, 1, 0.1),
  P      = c(.2, .5, .8)
)

@@

@@

TODO XXX: point out the claims they make.

@@

A naïve estimate would be that if e.g. 80 people of 100 report heads, then on average 50 really saw
heads and 60% (30/50) of the remainder are lying. More generally, from *R* reports of a good outcome
in a sample of size *N*, where the _bad_ outcome happens with probability *P*, we can estimate that
the following proportion are lying [@abeler2016preferences]:

\begin{equation}
\label{eqn:naive-estimator}
\frac{R/N - (1-P)}{P}
\end{equation}
The problem with this approach is that the number of heads is not
fixed. If we see 1 out of 3 people reporting heads, this method estimates there are less than zero
liars. But it is still possible that everyone saw heads and 1 person lied.

@@

sim_data <- tidyr::crossing(
  N      = params$N,
  lambda = params$lambda,
  P      = params$P
)

@@

sim_data %<>% mutate(
        heads = rbinom(nrow(.), N, 1 - P),
        lies = rbinom(nrow(.), N - heads, lambda),
        R    = heads + lies
      )

sim_data %<>% arrange(N, lambda, P)

nci_levels <- length(ci_levels)
sim_data <- sim_data[rep(1:nrow(sim_data), each = nci_levels), ]
sim_data$CI <- rep(ci_levels, nrow(sim_data)/nci_levels)

# algorithm is deterministic so we save time by 
# only printing out distinct lines
sim_input <- sim_data %>% 
      select(N, R, P, CI) %>% 
      distinct()

file_root <- "GSV-sims"
sim_output_file <- paste0(file_root, "Output.csv")
if (rerun_java) {
  sim_input_file <- paste0(file_root, ".csv")
  # input has to be in percentages:
  readr::write_csv(sim_input %>% mutate(P = P * 100), path = sim_input_file)

@@

```{r sanity-checks, include = FALSE, cache = cache_results}
sim_data %<>% mutate(
  expected_R = N * ((1 - P) + lambda * P)
)
summary(lm(R ~ expected_R, sim_data))
sim_data %>% 
      group_by(P, N) %>% 
      do(
        broom::tidy(lm(R ~ expected_R, .))
      ) %>% 
      filter(term == "expected_R")

@@

sim_est %<>% 
      mutate(p_pct = round(P * 100, 0)) %>% 
      left_join(gsv_estimates, by = c("N", "R", "p_pct" = "P", "CI")) %>% 
      mutate(p_pct = NULL)

@@

bayes_est <- sim_input %>% 
      rowwise() %>% 
      do({
        pstr <- update_prior(
                heads = .$R, 
                N = .$N, 
                P = .$P, 
                prior = my_prior
              )
        cis <- suppressWarnings(dist_hdr(pstr, .$CI/100))
        # calculate quantities as prop dishonest
        tibble(
          EV.ubayes = dist_mean(pstr),
          LB.ubayes = cis[1], 
          UB.ubayes = cis[2]
        )
      })
bayes_est <- cbind(sim_input, bayes_est)
sim_est <- left_join(sim_est, bayes_est, by = c("N", "P", "R", "CI"))

@@

simple_est <- sim_input %>%
      mutate(
        EV.simple = heads_to_liars(R/N, P)
      )

heads_confints <- apply(sim_input, 1, function (row) {
  ci <- binom.test(row["R"], row["N"], conf.level = row["CI"]/100)$conf.int
  res <- heads_to_liars(ci, row["P"])
  names(res) <- c("LB.simple", "UB.simple")
  res
})

@@

@@

sim_tmp <- sim_input[, c("R", "N", "P", "CI")]
recalc <- apply(sim_tmp, 1, function (x) {
  x <- c(
    prop_liars_ev_gsv(x["R"], x["N"], x["P"]),
    prop_liars_ci_gsv(x["CI"]/100, x["R"], x["N"], x["P"])
  )
  names(x) <- paste0(c("EV", "LB", "UB"), ".recalc")
  x
}) 
sim_tmp <- cbind(sim_tmp, t(recalc))
sim_est <- left_join(sim_est, sim_tmp, by = c("N", "P", "R", "CI"))

@@

sim_est %<>% mutate(
        within_ci = lambda >= LB & lambda <= UB,
        error     = EV - lambda,
        error_sq  = error^2
      )

@@

I ran simulations to check the overall performance of the GSV confidence intervals. Simulations
parameters are shown in Table \ref{tab:params-table}. For each parameter combination, I ran 1000
simulations. $\lambda$ is the probability that an individual in the sample lies and report heads
when they observe tails:

\begin{equation}
\label{eqn:lambda}
\lambda = \textrm{Prob}(i \textrm{ reports heads}|i\textrm{ saw tails}).
\end{equation}

For each simulation and confidence interval, I computed whether the confidence interval contained
the true value of $\lambda$. Table \ref{tab:coverage-just-gsv} shows the results.

@@

huxtable(
        Parameter = c(
          "Sample size (N)", 
          "Probability of lying ($\\lambda$)", 
          "Probability of bad random outcome (P)"
        ),
        Values    = c(
          paste(params$N, collapse = ", "),
          paste(params$lambda, collapse = ", "),
          paste(params$P, collapse = ", ")
        ),
        add_colnames = TRUE
      ) %>% 
      set_caption("Parameter values") %>% 
      set_escape_contents(everywhere, 1, FALSE) %>% 
      set_label("tab:params-table") %>% 
      theme_plain()
```

@@

ht_just_gsv <- ht_overall[1:2,]
label(ht_just_gsv) <- "tab:coverage-just-gsv"
ht_just_gsv[1, 1] <- ""
theme_plain(ht_just_gsv)
```

By definition, 95% of 95% confidence intervals ought to contain the true value, on average. This is
called "achieving nominal coverage". GSV intervals are far from this. The confidence intervals are
too narrow. This problem holds across all simulated probabilities of the low outcome, confidence
levels, and sample sizes.^[See the appendix.]

@@

\begin{equation}
\label{eqn:truncated-binom}
\textrm{Prob}(T \textrm{ heads}| R; N, P) = \frac{
  \textrm{binom}(T,N, 1 - P)
}{
  \sum^R_{k=0}\textrm{binom}(k,N, 1 - P)
}
\end{equation}

This is the binomial distribution, truncated at *R* because by assumption, nobody "lies downward"
and reports tails when they really saw heads.

Next, from *T* the number of lies told is calculated as $R - T$; and the proportion of lies told
is:

\begin{equation}
\textit{Lies} = \frac{R-T}{N-T} 
\end{equation}

because $N - T$ people saw the low outcome and had the chance to lie. Combining this
with the truncated binomial gives a cumulative distribution function of the proportion of liars.
This is then used to estimate means and confidence intervals.

Putting these together, for $R = N = 10$, the estimated distribution of liars is calculated as follows:

* With probability $\frac{1}{1024}$, there were really 10 heads. Nobody lied in the
sample.^[But the proportion of people who lied *out of those who saw tails* is undefined, because
noone saw tails. The GSV software seems to resolve this by fixing the proportion of lies to 100%.]

@@

```{r}

heads_10 <- sim_est %>% 
      filter(N == 10, R == 10, P == 0.5) %>% 
      select(lambda, heads) 
h10 <- heads_10$heads
l10 <- heads_10$lambda

inv_prob_h <- round(1/mean(h10 == 10), 0)
inv_prob_h_l20 <- round(1/mean(h10[l10 == 0.2] == 10), 0)

First, if 10 out of 10 heads are reported, you should learn two things. On the one hand, there are
probably many liars in your sample. On the other hand, probably a lot of coins really landed heads.
The probability distribution in (\ref{eqn:truncated-binom}) does not take account of this. In
particular, for *R = N*, it reduces to the binomial distribution. This is not correct. For example,
in my simulations with $P = 0.5$, the probability that there were 10 heads when $R = N = 10$ was
about 1 in `r inv_prob_h`, not 1 in 1024. When $\\lambda = 0.2$, it is about 1 in 
`r inv_prob_h_l20`. The same is true at the other end of the scale: when *R* is low, we indeed learn
that $T \le R$ but also that the overall distribution is not shaped like the prior.

Second, more importantly, the GSV approach estimates *Lies*, the distribution of the proportion of 
*lies actually told*, among the subsample of people who saw tails. But we are not usually interested
in the proportion of lies actually told. We care about the probability that people in the
sample would lie if they saw tails --  $\lambda$ in equation (\ref{eqn:lambda}). This $\lambda$ can
be interpreted in different ways. It could be that on seeing a tail, each person in the sample lies
with probability $\lambda$. Or it could be that the sample is drawn from a population of whom
$\lambda$ are (always) liars, and $1 - \lambda$ are truth-tellers.

The fact that some people saw heads, and had no reason to lie, is just a nuisance for estimation.
Similarly, we are not interested, per se, in whether more lies were actually told in one group than
another. Suppose that 9 out of 10 people saw heads. Only one person had a reason to lie, so by
definition, *Lies* will be either 0 or 1. This will almost certainly be different from the value of
*Lies* in another group where there were fewer heads. But that tells us very little, either about the 
samples as a whole, or about the population they come from.

*Lies* can be treated as an estimate of $\lambda$. It is unbiased, because the
probability that people would lie if they saw tails is independent of the coin flip they actually
see. But it can be a very noisy estimate. 
Again, suppose 10 heads out of 10 are reported, and 9 heads were really observed. *Lies* is 100%. 
But it is 100% of just one person.

The first of these two problems means that the GSV distribution of *Lies* is wrong. In the appendix
I show that their estimator can have substantial bias. In fact, it performs worse than the naïve
estimator from (\ref{eqn:naive-estimator}), $\frac{R-(1-P)}{P}$. Also, the GSV confidence intervals do not always achieve nominal coverage of *Lies*. When the number of heads reported is either high or low, the percentage of confidence intervals containing *Lies* may fall below the nominal value.

The second problem means that the GSV confidence intervals are not correct for $\lambda$. We can
tell that the second problem matters, because GSV coverage of $\lambda$ is much worse than coverage 
of *Lies*. Also, since the GSV estimator of *Lies* is biased, it is a biased estimator of
$\lambda$.

@@

as_huxtable(coverage_rn, add_colnames = TRUE) %>% 
      set_caption("GSV confidence interval coverage by proportion of heads reported") %>% 
      set_label("tab:coverage-rn") %>% 
      set_escape_contents(2:3, 1, FALSE) %>% 
      set_number_format(-1, -1, list(pct_format)) %>% 
      theme_plain() %>% 
      set_right_border(-1, 2, 0.4)
```

@@

Can we do better? Start with the probability of getting *R* reports of heads in total, given
$\lambda$. Since individuals report heads either if they see heads with probability $1-P$, or if
they see tails but lie, with probability $\lambda P$, this is just:

\begin{equation}
\textrm{Pr}(R|\lambda; N,P) = \textrm{binom}(R, N, (1 - P) + \lambda P)
\end{equation}

That immediately suggests the first method, which is to estimate the parameter of this distribution,
$(1 - P) + \lambda P$, from the proportion of heads reported in the sample, then back out $\lambda$.
This is the conventional method of e.g. @abeler2016preferences. It is justified if the sample is
large, because this will lessen sampling variation in the proportion of actual heads observed.
Similarly, if the sample is large enough, we can generate hypothesis tests for a value of $\lambda$
-- e.g., zero -- by using the tails of the binomial distribution. And we can back out confidence
bounds for $\lambda$ from confidence bounds for the population proportion of heads reported in the
same way. As GSV point out, in small samples, this method runs the risk that the sample proportion
of high outcomes will be different from its expected value.^[In particular, this method can estimate
confidence bounds for $\lambda$ lower than 0. If so, we can set them to 0.]   We'll see whether this
matters.

@@

The second method is to use Bayes' rule. Start with a prior probability density function over
the probability of liars, $\phi(\lambda)$. The posterior probability is then:

\begin{equation}
\phi(\lambda | R; N,P) = \frac{
  \textrm{Pr}(R|\lambda; N,P) \phi(\lambda)
}{
  \int_0^1 \textrm{Pr}(R|\lambda'; N,P) \phi(\lambda) \; \textrm{d}\lambda
}
\end{equation}

From this, one can derive confidence intervals and expected values in the usual way.^[R code
to do this is available at https://github.com/hughjonesd/GSV-comment. ] Technically,
they are Bayesian "credible" intervals. I use Highest Posterior Density intervals [@hyndman1996computing], rather than the central confidence interval. This allows the intervals
to include endpoints of the distribution, which is important when e.g. testing for $\lambda = 0$.

The Bayesian method requires a prior. Here, I used a uniform prior, $\phi(\lambda) = 1$ on $[0, 1]$.

I ran these estimation methods on my simulated data. Results are shown in Table
\ref{tab:coverage-allmethods}. Both frequentist and  Bayesian methods mostly achieve the nominal
confidence level, with more than 90/95/99% of intervals containing the true value of *Liars*. The
exception is the frequentist 99% confidence interval, which is too narrow.

@@

as_huxtable(coverage_N, add_colnames = TRUE) %>% 
      set_rowspan(c(2, 4, 6), "Method", 2) %>% 
      set_valign(c(2, 4, 6), "Method", "top") %>% 
      set_number_format(-1, contains("CI"), list(pct_format)) %>% 
      set_caption("Confidence interval coverage by sample size") %>% 
      set_label("tab:coverage-N") %>% 
      theme_plain() %>% 
      set_background_color(everywhere, 1, NA) %>% 
      set_top_border(c(4, 6), everywhere, 0.4) %>% 
      set_bottom_border(6, 1, 0.4)
```

@@

ggplot(nats, aes(x = factor(resnat, levels = resnat), y = mean, fill = mean)) +
      geom_col(alpha = 0.8) +
      geom_linerange(aes(ymin = ci.low,ymax = ci.high)) +
      geom_point(aes(y = prop_liars), shape = 4, size = 3, colour = "red") +
      xlab("Nation") + ylab("Prop. liars") +
      viridis::scale_fill_viridis(option = "E", guide = FALSE) + 
      coord_flip()

@@

Table \ref{tab:country-comparisons} shows Bayesian comparisons for selected countries. Even though
estimates have "shrunk" towards the pooled mean from the naive estimates, differences remain
significant, partly because the pooled prior has made posterior confidence intervals narrower.
Similarly, we can calculate the full distribution of the differences between countries.
